---
title: "p8105_hw4_mh4588 dashboard"
author: "Maggie Hsu"
date: "`r Sys.Date()`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)
library(p8105.datasets)
library(tidyverse)

data(rest_inspec)
```

```
Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}
#Boxplot comparing restaurant rating distributions by borough
rest_inspec |> #distribution of scores by borough
  filter(is.na(boro)==FALSE, boro != "Missing") |> #Remove NAs and  observations with missing borough values
  mutate(boro = fct_reorder(boro, score)) |> 
    plot_ly(y = ~score, color = ~boro, type = "box", colors = "viridis")
    
```

### Chart C

```{r}
#want to display number of critical warnings vs. number of non-critical warnings for restaurants of each grade
#also how to relabel legend and is this readable
rest_inspec |>
plot_ly(x = ~grade, y = ~as.factor(critical_flag), type = 'bar', name = 'Restaurant Grades vs.Warning Types', color=~critical_flag) |>
  layout(yaxis = list(title = 'Count'), barmode = 'group')

```
